### 2024-11-29 cv2/cv.tex
Update CV

\headleft{Personal information}
\MALE \\[0.5ex]
%Year of birth: \textbf{1861} \\[0.5ex]
\Letter\ Porto, {\bf Portugal} \\[0.5ex]
Citizenship: {\bf France} \\[0.5ex]
%Family: \textbf{Single without children} \\[0.5ex]
Languages: {\bf English} (fluent), {\bf French} (native).

@@

{\sc Head of Artificial Intelligence.} {\it Didimo}, Porto, Portugal. \hphantom{CACACACA} \dates{Sep 2019--present} \\
\smaller{Leading development of automated 3D character creation for {\em Popul8} software: shape reconstruction / generation, rig retargeting, skin texturing, asset fitting, mesh wrapping.}

\is % Item spacing -- defined in the preamble
{\sc Senior Computer Vision Scientist.} {\it CoVii (Ar\c celik group)}, Porto, Portugal. \dates{Feb 2017--Jul 2019} \\
\smaller{Developed embedded algorithms for smart domestic appliances: {\em VUXHub} and {\em Artisan oven} prototypes (demonstrated at IFA Berlin, 2017-18).}

@@

\is 
{\sc Scientific writing:} Author of 106 peer-reviewed scientific articles and 6 published international patents. 7847 citations, {\em h}-index: 35.

>>>>

\headleft{Personal information}
%\MALE \\[0.5ex]
%Year of birth: \textbf{1861} \\[0.5ex]
\Letter\ Porto, {\bf Portugal} \\[0.5ex]
Citizenship: {\bf France} \\[0.5ex]
%Family: \textbf{Single without children} \\[0.5ex]
Languages: {\bf English} (fluent), {\bf French} (native).

@@

{\sc Head of Artificial Intelligence.} {\it Didimo}, Porto, Portugal. \hphantom{CACACACA} \dates{Sep 2019--present} \\
\smaller{Leading development of automated 3D character creation for {\em Popul8} software: shape reconstruction / generation, skin texturing, asset fitting, autorigging, autoskinning, mesh shrink-wrapping.}

\is % Item spacing -- defined in the preamble
{\sc Senior Computer Vision Scientist.} {\it CoVii (Ar\c celik/Beko R\& D center)}, Porto, Portugal. \dates{Feb 2017--Jul 2019} \\
\smaller{Developed embedded ML algorithms for smart domestic appliances: {\em VUXHub} and {\em Artisan oven} prototypes (demonstrated at IFA Berlin, 2017-18).}

@@

\is 
{\sc Scientific writing:} Author of 106 peer-reviewed scientific articles and 6 published international patents. 8086 citations, {\em h}-index: 38.
